\chapter{Introduction}
\label{chap:introduction}

\section{Background}
\label{section:background}

The fitness industry has seen a significant surge in membership, yet the technological 
infrastructure within gyms remains largely stagnant. Most facilities still rely on manual 
equipment logging or basic membership check-ins. For members, the lack of real-time information 
regarding equipment availability leads to inefficient workouts and "availability uncertainty." 
For owners, the absence of granular data on how floor space is utilized results in suboptimal 
equipment purchasing and layout decisions. With the advancement of Computer Vision and the ubiquity 
of CCTV systems, there is a significant opportunity to transform passive video feeds into actionable 
spatial intelligence.

\section{Problem Statement}
\label{section:problem-statement}

Current gym operations suffer from two primary inefficiencies:

1. Member Frustration: Users often find their planned equipment occupied upon arrival, 
leading to routine disruption and decreased facility satisfaction.

2. Operational Blind Spots: Gym owners lack objective data on equipment utilization 
rates and "dead zones," forcing them to rely on guesswork for capital expenditure and floor plan optimization.

3. High Cost of Alternatives: Existing IoT sensor solutions are prohibitively expensive 
to install and maintain on every individual machine in a high-traffic environment.

\section{Solution Overview}
\label{section:solution-overview}

Prometheus solves these issues by implementing a non-intrusive AI system that utilizes existing 
gym CCTV cameras. The system uses an Edge-to-Cloud architecture where local processing units 
analyze video streams to identify machine states (Free vs. Occupied). This metadata is then 
synchronized to a cloud database, powering a real-time mobile tracker for members and a spatial 
analytics dashboard for management.

\subsection{Features}
\label{subsection:features}

\begin{enumerate}[leftmargin=90pt]
    \item \textbf{Real-time Occupancy Tracker:} A live mobile interface showing which machines are currently in use or available to help members plan their sets.
    \item \textbf{Spatial Heatmaps:} A web-based visual representation of high-traffic areas and underutilized equipment for facility owners.
    \item \textbf{AI Diet Estimator:} A database-driven tool that calculates nutritional needs and recommends food items based on user profiles.
    \item \textbf{Progress Logger:} A feature for members to record sets, reps, and weights, integrated with visual progress charts and historical data.
    \item \textbf{Workout Routine Generator:} An intelligent routine creator tailored to user goals, physical profile, and real-time equipment availability.
    \item \textbf{Automated Utilization Reports:} Weekly data summaries for owners regarding peak hours, machine popularity, and equipment ROI.
\end{enumerate}

\section{Target User}
\label{section:target-user}
The Prometheus system is designed for two distinct demographics, with a primary focus on facility management and business intelligence:

\begin{itemize}
    \item \textbf{Primary Users (Gym Owners and Facility Managers):} These are the central stakeholders 
    who utilize the system to drive operational efficiency. They require high-level spatial analytics to 
    identify equipment usage patterns, minimize "dead zones," and optimize facility layouts. By leveraging 
    the web-based dashboard, these users transform raw computer vision data into actionable business insights 
    to improve equipment Return on Investment (ROI) and long-term member retention.
    \item \textbf{Secondary Users (Gym-goers):} Individual patrons who benefit from the downstream data 
    generated by the system. These users range from beginners to advanced athletes who utilize the mobile 
    interface to minimize wait times and follow AI-generated routines. While they are frequent interactors 
    with the platform, their experience is an extension of the primary analytical framework established for 
    the facility.
\end{itemize}

\section{Terminology}
\label{section:terminology}
\begin{itemize}
    \item \textbf{Computer Vision (CV):} A field of Artificial Intelligence that enables computers to derive meaningful information from digital images or videos.
    \item \textbf{YOLO (You Only Look Once):} A state-of-the-art, real-time object detection system used by Prometheus for identifying equipment and patrons.
    \item \textbf{Edge Computing:} Processing data near the source (the camera) to reduce latency and enhance privacy by keeping raw video footage local.
    \item \textbf{Region of Interest (ROI):} Specifically defined coordinates within a video frame that correspond to individual pieces of gym equipment.
    \item \textbf{Occupancy Logic:} The algorithmic determination of a "busy" state based on the spatial intersection of "Person" and "Machine" detection boxes.
\end{itemize}